Summary of Survey Analysis NDNS carb50, 7 time slots

### 2018-08-05 paper/main.tex
LCGA removed
method updated regression models started writing some variables changed to log-transformed

%\usepackage[table]{xcolor}
\usepackage{colortbl} % to use colors for tables
\usepackage[usestackEOL]{stackengine} %to change lines within a cell in the table
\usepackage{caption} % to change the font of the table titles

%----------------------------------------------------------------------------------------
%	MARGIN SETTINGS
%----------------------------------------------------------------------------------------

@@

\thesistitle{The timing of carbohydrate intake in UK adults, using the National Dietary and Nutrition Survey (NDNS) 2008-2014 programme} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Professor Luigi \textsc{Palla}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
\degree{MSc in Medical Statistics} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{Chaochen \textsc{Wang}} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

@@

\textbf{AIC} & \textbf{A}kaike \textbf{I}information \textbf{C}riterion \\
\textbf{aBIC} & \textbf{a}djusted \textbf{B}ayesian \textbf{I}nformation \textbf{C}riterion \\
\textbf{BMI} & \textbf{B}ody \textbf{M}ass \textbf{I}ndex \\
%\textbf{cAIC} & \textbf{c}onsistent \textbf{A}kaike \textbf{I}nformation \textbf{C}riterion \\
\textbf{BIC} & \textbf{B}ayesian \textbf{I}information \textbf{C}riterion \\
\textbf{DM}  & \textbf{D}iabetes \textbf{M}ellitus \\
\textbf{EM}  & \textbf{E}xpectation \textbf{M}aximazation  \\
\textbf{FSA} & \textbf{F}ood \textbf{S}tandards \textbf{A}gency  \\
\textbf{HbA1c} & \textbf{H}emoglobin \textbf{A1c}: Glycated hemoglobin \\
\textbf{LCA} & \textbf{L}atent \textbf{C}lass \textbf{A}nalysis\\
\textbf{LCGA} & \textbf{L}atent \textbf{C}lass \textbf{G}rowth \textbf{A}nalysis \\
%\textbf{LTA} & \textbf{L}atent \textbf{T}ransition \textbf{A}nalysis \\
\textbf{MAFF} & \textbf{M}inistry of \textbf{A}griculture, \textbf{F}isheries and \textbf{F}ood \\
\textbf{MAR} & \textbf{M}issing \textbf{A}t \textbf{R}andom \\
\textbf{MCAR} & \textbf{M}issing \textbf{C}ompletely \textbf{A}t \textbf{R}andom \\
\textbf{MLCA} & \textbf{M}ultilevel \textbf{L}atent \textbf{C}lass \textbf{A}nalysis \\
\textbf{MNAR} & \textbf{M}issing \textbf{N}ot \textbf{A}t \textbf{R}andom \\
\textbf{ML} & \textbf{M}aximum \textbf{L}ikelihood \\
\textbf{NDNS} & the \textbf{N}ational \textbf{D}ietary and \textbf{N}utrition \textbf{S}urvey \\
\textbf{OR} & \textbf{O}dds \textbf{R}atio \\
\textbf{PHE} & \textbf{P}ublic \textbf{H}ealth \textbf{E}ngland  \\
\textbf{PSUs} & \textbf{P}rimary \textbf{S}ampling \textbf{U}nits \\
\end{abbreviations}

>>>>

%\usepackage[table]{xcolor}
\usepackage{colortbl} % to use colors for tables
\usepackage[usestackEOL]{stackengine} %to change lines within a cell in the table
\usepackage{caption} % to change the font of the table titles
\usepackage{amssymb} % to use \leqslant
%----------------------------------------------------------------------------------------
%	MARGIN SETTINGS
%----------------------------------------------------------------------------------------

@@

\thesistitle{The timing of carbohydrate intake in UK adults, using the National Dietary and Nutrition Survey (NDNS) 2008/09-2015/16 programme} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Professor Luigi \textsc{Palla}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
\degree{MSc in Medical Statistics} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{Chaochen \textsc{Wang}} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

@@

%\textbf{AIC} & \textbf{A}kaike \textbf{I}information \textbf{C}riterion \\
%\textbf{aBIC} & \textbf{a}djusted \textbf{B}ayesian \textbf{I}nformation \textbf{C}riterion \\
\textbf{BMI} & \textbf{B}ody \textbf{M}ass \textbf{I}ndex \\
%\textbf{cAIC} & \textbf{c}onsistent \textbf{A}kaike \textbf{I}nformation \textbf{C}riterion \\
\textbf{BIC} & \textbf{B}ayesian \textbf{I}information \textbf{C}riterion \\
\textbf{DM}  & \textbf{D}iabetes \textbf{M}ellitus \\
\textbf{EM}  & \textbf{E}xpectation \textbf{M}aximazation  \\
\textbf{FSA} & \textbf{F}ood \textbf{S}tandards \textbf{A}gency  \\
\textbf{A1c} & Haemoglobin \textbf{A1c}: Glycated hemoglobin \\
\textbf{LCA} & \textbf{L}atent \textbf{C}lass \textbf{A}nalysis\\
%\textbf{LCGA} & \textbf{L}atent \textbf{C}lass \textbf{G}rowth \textbf{A}nalysis \\
%\textbf{LTA} & \textbf{L}atent \textbf{T}ransition \textbf{A}nalysis \\
\textbf{MAFF} & \textbf{M}inistry of \textbf{A}griculture, \textbf{F}isheries and \textbf{F}ood \\
%\textbf{MAR} & \textbf{M}issing \textbf{A}t \textbf{R}andom \\
%\textbf{MCAR} & \textbf{M}issing \textbf{C}ompletely \textbf{A}t \textbf{R}andom \\
\textbf{MLCA} & \textbf{M}ultilevel \textbf{L}atent \textbf{C}lass \textbf{A}nalysis \\
%\textbf{MNAR} & \textbf{M}issing \textbf{N}ot \textbf{A}t \textbf{R}andom \\
\textbf{ML} & \textbf{M}aximum \textbf{L}ikelihood \\
\textbf{NDNS} & the \textbf{N}ational \textbf{D}ietary and \textbf{N}utrition \textbf{S}urvey \\
\textbf{OR} & \textbf{O}dds \textbf{R}atio \\
\textbf{PHE} & \textbf{P}ublic \textbf{H}ealth \textbf{E}ngland  \\
\textbf{PSUs} & \textbf{P}rimary \textbf{S}ampling \textbf{U}nits \\
\end{abbreviations}

### 2018-08-05 results/table1slots.Rmd
method updated regression models started writing some variables changed to log-transformed

BMI78 <- blood78 %>% 
  select(ID, Sex, age, bmival, wstval, Diabetes, bpmedc2, bpmedd2, hyper140_2, hibp140_2,  
         Glucose, A1C, cigsta3, dnoft3, dnnow, wti_Y78, wtn_Y78, wtb_Y78, ethgrp5, ethgrp2,
         cluster1, cluster2, cluster3, nssec8, paidemployment, qual7, eqvinc, MarSt2,
         cluster4, cluster5, area, gor) %>% 
  rename(wti = wti_Y78, wtn = wtn_Y78, wtb = wtb_Y78, drink = dnoft3) %>% 
  mutate(Years = "7-8", MVPAtime = NA, MarStat = NA) %>% 
  replace_with_na(replace = list(bmival = -1, qual7 = -8,
                                 wstval = -1, eqvinc = -1,
                                 bpmedd2 = -1, MarSt2 = -1,
                                 bpmedc2 = -1,
                                 hyper140_2 = -7, 
                                 # hyper140_2 = -1, 
                                 hibp140_2 = -7, 
                                 # hibp140_2 = -1, 
                                 Glucose = -1, 
                                 A1C  = -1, 
                                 dnnow = -1,
                                 drink = -1,
                                 ethgrp5 = -4,
                                 ethgrp2 = -4,
                                 cigsta3 = -1, 
                                 nssec8 = -9, 
                                 paidemployment = -1)) %>% 
  replace_with_na(replace = list(hyper140_2 = -1, hibp140_2 = -1, nssec8 = 99, qual7 = -1,
                                 drink = -8, ethgrp2 = -9, ethgrp5 = -9)) %>% 
    replace_with_na(replace = list(drink = -9, ethgrp2 = -8, ethgrp5 = -8,
                                 cigsta3 = -8)) %>% 
  replace_with_na(replace = list(ethgrp2 = -1, ethgrp5 = -1))

BMI56 <- blood56 %>% 
  select(ID, Sex, age, area, bmival, wstval, Diabetes, bpmedc2, bpmedd2, hyper140_2, hibp140_2, MVPAtime,
         Glucose, A1C, cigsta3, dnoft3, dnnow, wti_Y56, wtn_Y56, wtb_Y56, ethgrp5, ethgrp2, qual7,
         cluster1, cluster2, cluster3, nssec8, paidemployment, eqvinc, MarSt2,
         cluster4, cluster5, area, gor) %>% 
  mutate(Years = "5-6", MarStat = NA) %>% 
  rename(wti = wti_Y56, wtn = wtn_Y56, wtb = wtb_Y56, drink = dnoft3) %>% 
  replace_with_na(replace = list(bmival = -1, paidemployment = -9,
                                 wstval = -1, qual7 = -8,
                                 bpmedd2 = -1, eqvinc = -1,
                                 bpmedc2 = -1, MarSt2 = -1,
                                 hyper140_2 = -7, 
                                 # hyper140_2 = -1, 
                                 hibp140_2 = -7, 
                                 # hibp140_2 = -1, 
                                 Glucose = -1, 
                                 A1C  = -1, 
                                 dnnow = -1,
                                 drink = -1,
                                 ethgrp5 = -4,
                                 ethgrp2 = -4,
                                 cigsta3 = -1,
                                 MVPAtime = -1, 
                                 nssec8 = -9)) %>% 
  replace_with_na(replace = list(hyper140_2 = -1, hibp140_2 = -1, paidemployment = -8,
                                 drink = -8, nssec8 = 99)) %>% 
    replace_with_na(replace = list(drink = -9, paidemployment = -1, qual7 = -1,
                                 cigsta3 = -8))

BMI14 <- blood14 %>% 
  select(ID, Sex, age, bmival, wstval, Diabetes, bpmedc, bpmedd, hyper140, hibp140, MVPAtime,
         Glucose, A1C, cigsta3, dnoft3, dnnow, wti_CY1234, wtn_CY1234, wtb_CY1234, ethgr5, ethgr2,
         cluster, area, gor, nssec8, paidemployment, qual7, eqvinc, MarSt2, MarStat) %>%
  rename(hyper140_2 = hyper140, hibp140_2 = hibp140, bpmedd2 = bpmedd, 
         bpmedc2 = bpmedc, cluster1 = cluster, ethgrp5 = ethgr5, ethgrp2 = ethgr2, 
         wti = wti_CY1234, wtn = wtn_CY1234, wtb =  wtb_CY1234, drink = dnoft3) %>% 
  mutate(cluster2 = NA, cluster3 = NA, cluster4 = NA, cluster5 = NA, Years = "1-4") %>% 
  replace_with_na(replace = list(bmival = -1, paidemployment = -9, 
                                 wstval = -1, qual7 = -8,
                                 bpmedd2 = -1, eqvinc = -1,
                                 bpmedc2 = -1, MarSt2 = -4, 
                                 hyper140_2 = -7, MarStat = -4,
                                 # hyper140_2 = -1, 
                                 hibp140_2 = -7, 
                                 # hibp140_2 = -1, 
                                 Glucose = -1, 
                                 A1C  = -1, 
                                 dnnow = -1,
                                 drink = -1,
                                 ethgrp5 = -4,
                                 ethgrp2 = -4,
                                 cigsta3 = -1,
                                 MVPAtime = -4, 
                                 nssec8 = -8)) %>% 
  replace_with_na(replace = list(hyper140_2 = -1, hibp140_2 = -1, MVPAtime = -1, paidemployment = -8,
                                 drink = -8, nssec8 = -1, qual7 = -1, MarSt2 = -1)) %>% 
  replace_with_na(replace = list(drink = -9, paidemployment = -4,
                                 cigsta3 = -8, nssec8 = 99)) %>% 
  replace_with_na(replace = list(paidemployment = -1))

@@

Energy14 <- food14 %>% 
  select(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, CHOpctotE, Proteing, ProteinpctotE, 
         Fatg, FatpctotE)
Energy14$Country[Energy14$Country == "Northern Ireland"] <- "NI"

Energy56 <- food56 %>% 
  select(ID, Country, Surveyyear, EnergykJ, Carbohydrateg, CHOpctotE, Proteing, ProteinpctotE, 
         Fatg, FatpctotE) %>% 
  rename(SurveyYear = Surveyyear)

Energy78 <- food78 %>% 
  select(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, CHOpctotE, Proteing, ProteinpctotE, 
         Fatg, FatpctotE)

@@

>>>>

BMI78 <- blood78 %>% 
  select(ID, Sex, age, bmival, wstval, Diabetes, bpmedc2, bpmedd2, hyper140_2, hibp140_2,  
         Glucose, A1C, cigsta3, dnoft3, dnnow, wti_Y78, wtn_Y78, wtb_Y78, ethgrp5, ethgrp2,
         cluster1, cluster2, cluster3, nssec8, paidemployment, qual7, eqvinc, MarSt2,
         cluster4, cluster5, area, gor, LDL, HDL, Chol, Trig) %>% 
  rename(wti = wti_Y78, wtn = wtn_Y78, wtb = wtb_Y78, drink = dnoft3) %>% 
  mutate(Years = "7-8", MVPAtime = NA, MarStat = NA) %>% 
  replace_with_na(replace = list(bmival = -1, qual7 = -8,
                                 wstval = -1, eqvinc = -1,
                                 bpmedd2 = -1, MarSt2 = -1,
                                 bpmedc2 = -1,
                                 hyper140_2 = -7, 
                                 # hyper140_2 = -1, 
                                 hibp140_2 = -7, 
                                 # hibp140_2 = -1, 
                                 Glucose = -1, 
                                 A1C  = -1, 
                                 LDL = -1, HDL = -1, Chol = -1, Trig = -1,
                                 dnnow = -1,
                                 drink = -1,
                                 ethgrp5 = -4,
                                 ethgrp2 = -4,
                                 cigsta3 = -1, 
                                 nssec8 = -9, 
                                 paidemployment = -1)) %>% 
  replace_with_na(replace = list(hyper140_2 = -1, hibp140_2 = -1, nssec8 = 99, qual7 = -1,
                                 drink = -8, ethgrp2 = -9, ethgrp5 = -9)) %>% 
    replace_with_na(replace = list(drink = -9, ethgrp2 = -8, ethgrp5 = -8,
                                 cigsta3 = -8)) %>% 
  replace_with_na(replace = list(ethgrp2 = -1, ethgrp5 = -1))

BMI56 <- blood56 %>% 
  select(ID, Sex, age, area, bmival, wstval, Diabetes, bpmedc2, bpmedd2, hyper140_2, hibp140_2, MVPAtime,
         Glucose, A1C, cigsta3, dnoft3, dnnow, wti_Y56, wtn_Y56, wtb_Y56, ethgrp5, ethgrp2, qual7,
         cluster1, cluster2, cluster3, nssec8, paidemployment, eqvinc, MarSt2,
         cluster4, cluster5, area, gor, LDL, HDL, Chol, Trig) %>% 
  mutate(Years = "5-6", MarStat = NA) %>% 
  rename(wti = wti_Y56, wtn = wtn_Y56, wtb = wtb_Y56, drink = dnoft3) %>% 
  replace_with_na(replace = list(bmival = -1, paidemployment = -9,
                                 wstval = -1, qual7 = -8,
                                 bpmedd2 = -1, eqvinc = -1,
                                 bpmedc2 = -1, MarSt2 = -1,
                                 hyper140_2 = -7, 
                                 # hyper140_2 = -1, 
                                 hibp140_2 = -7, 
                                 # hibp140_2 = -1, 
                                 Glucose = -1, 
                                 A1C  = -1, 
                                 dnnow = -1,
                                 drink = -1,
                                 ethgrp5 = -4,
                                 ethgrp2 = -4,
                                 LDL = -1, HDL = -1, Chol = -1, Trig = -1,
                                 cigsta3 = -1,
                                 MVPAtime = -1, 
                                 nssec8 = -9)) %>% 
  replace_with_na(replace = list(hyper140_2 = -1, hibp140_2 = -1, paidemployment = -8,
                                 drink = -8, nssec8 = 99)) %>% 
    replace_with_na(replace = list(drink = -9, paidemployment = -1, qual7 = -1,
                                 cigsta3 = -8))

BMI14 <- blood14 %>% 
  select(ID, Sex, age, bmival, wstval, Diabetes, bpmedc, bpmedd, hyper140, hibp140, MVPAtime,
         Glucose, A1C, cigsta3, dnoft3, dnnow, wti_CY1234, wtn_CY1234, wtb_CY1234, ethgr5, ethgr2,
         cluster, area, gor, nssec8, paidemployment, qual7, eqvinc, MarSt2, MarStat, LDL, HDL, Chol, Trig) %>%
  rename(hyper140_2 = hyper140, hibp140_2 = hibp140, bpmedd2 = bpmedd, 
         bpmedc2 = bpmedc, cluster1 = cluster, ethgrp5 = ethgr5, ethgrp2 = ethgr2, 
         wti = wti_CY1234, wtn = wtn_CY1234, wtb =  wtb_CY1234, drink = dnoft3) %>% 
  mutate(cluster2 = NA, cluster3 = NA, cluster4 = NA, cluster5 = NA, Years = "1-4") %>% 
  replace_with_na(replace = list(bmival = -1, paidemployment = -9, 
                                 wstval = -1, qual7 = -8,
                                 bpmedd2 = -1, eqvinc = -1,
                                 bpmedc2 = -1, MarSt2 = -4, 
                                 hyper140_2 = -7, MarStat = -4,
                                 # hyper140_2 = -1, 
                                 hibp140_2 = -7, 
                                 # hibp140_2 = -1, 
                                 Glucose = -1, 
                                 A1C  = -1, 
                                 dnnow = -1,
                                 LDL = -1, HDL = -1, Chol = -1, Trig = -1,
                                 drink = -1,
                                 ethgrp5 = -4,
                                 ethgrp2 = -4,
                                 cigsta3 = -1,
                                 MVPAtime = -4, 
                                 nssec8 = -8)) %>% 
  replace_with_na(replace = list(hyper140_2 = -1, hibp140_2 = -1, MVPAtime = -1, paidemployment = -8,
                                 drink = -8, nssec8 = -1, qual7 = -1, MarSt2 = -1)) %>% 
  replace_with_na(replace = list(drink = -9, paidemployment = -4,
                                 cigsta3 = -8, nssec8 = 99)) %>% 
  replace_with_na(replace = list(paidemployment = -1))

@@

Energy14 <- food14 %>% 
  select(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, 
         CHOpctotE, Proteing, ProteinpctotE, Alcoholg, AlcoholpctotE,
         Fatg, FatpctotE)
Energy14$Country[Energy14$Country == "Northern Ireland"] <- "NI"

Energy56 <- food56 %>% 
  select(ID, Country, Surveyyear, EnergykJ, Carbohydrateg, 
         CHOpctotE, Proteing, ProteinpctotE, Alcoholg, AlcoholpctotE,
         Fatg, FatpctotE) %>% 
  rename(SurveyYear = Surveyyear)

Energy78 <- food78 %>% 
  select(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, 
         CHOpctotE, Proteing, ProteinpctotE, Alcoholg, AlcoholpctotE,
         Fatg, FatpctotE)

@@

CW3CB3 <- read_table2("~/Documents/LSHTMproject/results/Timeslots/NDNSslot_CW3CB3.txt",  
                              col_names = FALSE)# change the path to your own path

names(CW3CB3) <- c("Breakfast", "Morning.snack", "Lunch",
                   "Afternoon.snack", "Dinner", "Before.bedtime.snack",
                   "Midnight.food", "ID_DAY", "AGE", "SEX", "CPROB1",
                      "CPROB2", "CPROB3", "CPROB4", "CPROB5", "CPROB6", 
                      "CPROB7", "CPROB8", "CPROB9", 
                      "CB", "CW", "MLCJOINT", "ID")
